Covariate Analysis of ROSMAP Reprocessed counts

### 2020-12-23 code/2020_12_09_ROSMAP_RinEQGt5Cohort_sageseqr_hg38.Rmd
update CasevCntrl

>>>>

clean_md$diagnosis <- as.character('OTHER')
clean_md$diagnosis[ as.numeric(as.character(clean_md$cogdx)) == 1 & 
                    as.numeric(as.character(clean_md$braaksc)) <= 3 & 
                    as.numeric(as.character(clean_md$ceradsc)) >= 3] <- as.character('CONTROL')

clean_md$diagnosis[as.numeric(as.character(clean_md$cogdx)) == 4&
                   as.numeric(as.character(clean_md$braaksc)) >= 4 & 
                   as.numeric(as.character(clean_md$ceradsc)) <= 2] = as.character('AD')
clean_md$diagnosis <- as.factor(clean_md$diagnosis)

import_metadata$diagnosis <- as.character('OTHER')
import_metadata$diagnosis[ as.numeric(as.character(import_metadata$cogdx)) == 1 & 
                           as.numeric(as.character(import_metadata$braaksc)) <= 3 &
                           as.numeric(as.character(import_metadata$ceradsc)) >= 3 ] = 'CONTROL'

import_metadata$diagnosis[ as.numeric(as.character(import_metadata$cogdx)) == 4 & 
                           as.numeric(as.character(import_metadata$braaksc)) >= 4 & 
                           as.numeric(as.character(import_metadata$ceradsc)) <= 2] = 'AD'
import_metadata$diagnosis <- as.factor(import_metadata$diagnosis)
